### 2023-03-15 manuscript.tex
Merge pull request #4 from MMV-Lab/polish [ci skip]
This build is based on
https://github.com/MMV-Lab/im2im-paper/commit/e303b22eb8e0a0ae107c7f0793dfcfb7a1f40736.

This commit was created by the following CI build and job:
https://github.com/MMV-Lab/im2im-paper/commit/e303b22eb8e0a0ae107c7f0793dfcfb7a1f40736/checks
https://github.com/MMV-Lab/im2im-paper/actions/runs/4426991319

This manuscript
(\href{https://MMV-Lab.github.io/im2im-paper/v/c32563406547c62b8e0e04e565d02aabdeac9843/}{permalink})
was automatically generated
from \href{https://github.com/MMV-Lab/im2im-paper/tree/c32563406547c62b8e0e04e565d02aabdeac9843}{MMV-Lab/im2im-paper@c325634}
on March 14, 2023.

@@

\begin{itemize}
\item
  \textbf{Justin Sonneck}
  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
  \href{https://orcid.org/0000-0002-1640-3045}{0000-0002-1640-3045}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
  \href{https://github.com/Justin-Sonneck}{Justin-Sonneck}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/twitter.svg}
  \href{https://twitter.com/JustinSonneck}{JustinSonneck}
  Leibniz-Institut für Analytische Wissenschaften - ISAS - e.V.
  · Funded by The Federal Ministry of Education and Research (BMBF) under the funding reference 161L0272
\item
  \textbf{Jianxu Chen}
  \textsuperscript{\protect\hyperlink{correspondence}{✉}}
  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
  \href{https://orcid.org/0000-0002-8500-1357}{0000-0002-8500-1357}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
  \href{https://github.com/jxchen01}{jxchen01}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/twitter.svg}
  \href{https://twitter.com/JianxuChen}{JianxuChen}
  Leibniz-Institut für Analytische Wissenschaften - ISAS - e.V.
  · Funded by The Federal Ministry of Education and Research (BMBF) under the funding reference 161L0272
\end{itemize}

@@

The deep learning research in computer vision has been growing extremely fast in the past decade, many of which have been translated into novel image analysis methods for biomedical problems. Broadly speaking, many deep learning based biomedical image analysis methods can be considered as a general image-to-image transformation framework. In this work, we introduce a new open source python package \textbf{MMV\_Im2Im} for image-to-image transformation in bioimaging applications. The overall package is designed with a generic image-to-image transformation framework, which could be directly used for semantic segmentation, instance segmentation, image restoration, image generation, etc. The implementation takes advantage of the state-of-the-art machine learning engineering techniques for users to focus on the research without worrying about the engineering details. We demonstrate the effectiveness of \textbf{MMV\_Im2Im} in more than ten different biomedical problems. For biomedical machine learning researchers, we hope this new package could serve as the starting point for their specific problems to stimulate new biomedical image analysis or machine learning methods. For experimental biomedical researchers, we hope this work can provide a holistic view of the image-to-image transformation concept with diverse examples, so that deep learning based image-to-image transformation could be further integrated into the assay development process and permit new biomedical studies that can hardly be done only with traditional experimental methods. Source code can be found at \url{https://github.com/MMV-Lab/mmv_im2im}.

@@

>>>>

This manuscript
(\href{https://MMV-Lab.github.io/im2im-paper/v/e303b22eb8e0a0ae107c7f0793dfcfb7a1f40736/}{permalink})
was automatically generated
from \href{https://github.com/MMV-Lab/im2im-paper/tree/e303b22eb8e0a0ae107c7f0793dfcfb7a1f40736}{MMV-Lab/im2im-paper@e303b22}
on March 15, 2023.

@@

\begin{itemize}
\item
  \textbf{Justin Sonneck}
  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
  \href{https://orcid.org/0000-0002-1640-3045}{0000-0002-1640-3045}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
  \href{https://github.com/Justin-Sonneck}{Justin-Sonneck}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/twitter.svg}
  \href{https://twitter.com/JustinSonneck}{JustinSonneck}
  Leibniz-Institut für Analytische Wissenschaften - ISAS - e.V., Dortmund 44139, Germany
\item
  \textbf{Jianxu Chen}
  \textsuperscript{\protect\hyperlink{correspondence}{✉}}
  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
  \href{https://orcid.org/0000-0002-8500-1357}{0000-0002-8500-1357}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
  \href{https://github.com/jxchen01}{jxchen01}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/twitter.svg}
  \href{https://twitter.com/JianxuChen}{JianxuChen}
  Leibniz-Institut für Analytische Wissenschaften - ISAS - e.V., Dortmund 44139, Germany
\end{itemize}

@@

Over the past decade, deep learning (DL) research in computer vision has been growing rapidly, with many advances in DL-based image analysis methods for biomedical problems. In this work, we introduce MMV\_Im2Im, a new open-source python package for image-to-image transformation in bioimaging applications. MMV\_Im2Im is designed with a generic image-to-image transformation framework that can be used for a wide range of tasks, including semantic segmentation, instance segmentation, image restoration, and image generation, etc.. Our implementation takes advantage of state-of-the-art machine learning engineering techniques, allowing researchers to focus on their research without worrying about engineering details. We demonstrate the effectiveness of MMV\_Im2Im on more than ten different biomedical problems, showcasing its general potentials and applicabilities.

For computational biomedical researchers, MMV\_Im2Im provides a starting point for developing new biomedical image analysis or machine learning algorithms, where they can either reuse the code in this package or fork and extend this package to facilitate the development of new methods. Experimental biomedical researchers can benefit from this work by gaining a comprehensive view of the image-to-image transformation concept through diversified examples and use cases. We hope this work can give the community inspirations on how DL-based image-to-image transformation can be integrated into the assay development process, enabling new biomedical studies that cannot be done only with traditional experimental assays. To help researchers get started, we have provided source code, documentation, and tutorials for MMV\_Im2Im at https://github.com/MMV-Lab/mmv\_im2im under MIT license.

\hypertarget{keywords}{%
\subsection{Keywords}\label{keywords}}

Deep learning, biomedical image analysis, image-to-image transformation, open-source

@@

\hypertarget{code-and-data-availability}{%
\subsection{Code and data availability}\label{code-and-data-availability}}

Project name: MMV\_Im2Im (Microscopy Machine Vision, Image-to-Image transformation)

Project home page: https://github.com/mmv-lab/mmv\_im2im
Operating system(s): Linux and Windows (when using GPU), also MacOS (when only using CPU)
Programming language: Python
Other requirements: PyTorch 1.11 or higher, all other dependencies are specified as in https://github.com/MMV-Lab/mmv\_im2im/blob/main/setup.py
License: MIT license
